Generative Adversarial Networks

### 2017-11-13 cs6735/project/draft.tex
add algorithm

\usepackage{natbib}
\usepackage{graphicx}

\usepackage{parskip}

@@

\section{Background}

>>>>

\usepackage{natbib}
\usepackage{graphicx}
\usepackage[options ]{algorithm2e}
\usepackage{parskip}

@@

\section{Background}
hello

\begin{algorithm}[H]
  \SetAlgoLined
  \Input{$n$: The number of training iterations} \linebreak
  \Input{$k$: The number of discriminator iterations} \linebreak
  \For{training iteration in n} {
    \For{discriminator iteration in k} {
      sample $m$ vectors $\{z^{(1)},...,z^{(m)}\}$ from distribution $p_z(z)$\;
      sample $m$ vectors $\{x^{(1)},...,x^{(m)}\}$ from the training samples\;
      update the discriminator using its stochastic gradient
      $$\nabla_{\theta_d}\frac{1}{m}\sum_{i=1}^{m}[\log(D(x^{(i)}))+\log(1-D(G(z^{(i)})))]$$
    }
    sample $m$ vectors $\{z^{(1)},...,z^{(m)}\}$ from distribution $p_z(z)$\;
    update the generator using its stochastic gradient\;
    $$\nabla_{\theta_g}\frac{1}{m}\sum_{i=1}^{m}[\log(1-D(G(z^{(i)})))]$$
  }
  \caption{The initial generative adversarial network algorithm developed by Goodfellow \textit{et al.} in 2014 \citep{2014arXiv1406.2661G}. Multiple variations of this algorithm have since been produced. One of the benefits of adversarial networks is that they may be updated using regular gradient descent.}
\end{algorithm}

This algorithm presents the initial training algorithm used by Goodfellow \textit{et al.} when GANs were introduced in 2014 \citep{2014arXiv1406.2661G}. Many modifications have been made by various sources. The first step in the algorithm is to optimize the discriminator $D$. Optimally, one would train $D$ to completion; however, this is unrealistic in practice. The number of discriminator training iterations becomes a hyperparameter of the algorithm. For the initial GAN experiments, this number was set to $1$ to reduce computation time.

\section{Issues}
Generative adversarial networks are often characterized by their instability. The training process of

Shape, count, orientation

\section{Improvements}

\section{Model Variations}

\section{Research Frontiers}
